Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-20 paper/tex/sections/appendix.tex
trim old bits

\subsection{Normalisation summary}
Finally, we can substitute Equations~\ref{eq:norm_avg_target_formation} and \ref{eq:m_SF_MW} into \ref{eq:norm_frame} and write that the overall normalisation of the detection rate is calculated as
\begin{align}
    N_{\rm detect} &= f_{\rm detect} \cdot 9.1 \times 10^{10} \unit{M_{\odot}} \nonumber \\
    &\times \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \nonumber \\
    &\times \qty(\frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i)^{-1}.
\end{align}

>>>>

\subsection{Normalisation summary}
Finally, we can substitute Equations~\ref{eq:norm_avg_target_formation} and \ref{eq:m_SF_MW} into \ref{eq:norm_frame} and write that the overall normalisation of the detection rate is calculated as
\begin{align}
    N_{\rm detect} &= f_{\rm detect} \cdot 10.4 \times 10^{10} \unit{M_{\odot}} \nonumber \\
    &\times \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \nonumber \\
    &\times \qty(\frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i)^{-1}.
\end{align}
